Balance responses in MS

### 2020-01-28 R/msBalance.Rmd
added call to preprocessData.m

## Data processing
Each individual EMG record was registered to the onset of platform motion and resampled to a common timebase

>>>>

## Data processing
Each individual EMG record was registered to the onset of treadmill motion and resampled to a common timebase.

```{r}
# if trial-level data files do not exist, run matlab batch steps to populate them
if (!file.exists("../tmp/Treadmill.csv")){
  system(paste(matlabCommand, "'cd ../m; preprocessData; exit'"))
}
```
